On Logic Embeddings and G\"odel's God

### 2015-04-05 Papers/2014/WADT/WADT-4pages.tex
Add citation of CSR paper

In recent work \cite{C40,J28} we have applied the embedding approach
to verify and automate a philosophical argument that has fascinated
philosophers and theologians for about 1000 years: the ontological
argument for the existence of God~\cite{sobel2004logic}. We have
thereby concentrated on G\"odel's \cite{GoedelNotes} 
modern version of this argument and on
Scott's \cite{ScottNotes} modification, which
employ a second-order modal logic (S5) for which, until now, no
theorem provers were available.  In our computer-assisted study of the
argument, the HOL provers LEO-II \cite{C26}, Satallax \cite{Satallax}
and Nitpick \cite{Nitpick} have made some interesting observations,
some of which were unknown so far. This is a landmark result, with
media repercussion in a global scale, and yet it is only a glimpse of
what can be achieved by combining computer science, philosophy and
theology.

>>>>

In recent work \cite{C40,J28,CSR} we have applied the embedding approach
to verify and automate a philosophical argument that has fascinated
philosophers and theologians for about 1000 years: the ontological
argument for the existence of God~\cite{sobel2004logic}. We have
thereby concentrated on G\"odel's \cite{GoedelNotes} 
modern version of this argument and on
Scott's \cite{ScottNotes} modification, which
employ a second-order modal logic (S5) for which, until now, no
theorem provers were available.  In our computer-assisted study of the
argument, the HOL provers LEO-II \cite{C26}, Satallax \cite{Satallax}
and Nitpick \cite{Nitpick} have made some interesting observations,
some of which were unknown so far. This is a landmark result, with
media repercussion in a global scale, and yet it is only a glimpse of
what can be achieved by combining computer science, philosophy and
theology.
